# Basic Inferential Data Analysis of ToothGrowth data using R
#Summary
The response is the length of odontoblasts(cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of the three dose levels of vitamin C(0.5,1 and 2 mg/day) by one of tow delivery methods, orange juice or ascorbic acid(a form of vitamin C and coded as VC).

There are 60 observations and 3 variables.
Variables are:
1. len: numeric Tooth length
2. supp factor: Supplement type(VC or OJ)
3. dose: numeric Dose in milligrams/day

```{r,eval=FALSE}
library(UsingR)
```

#Dataset
```{r}
data("ToothGrowth")
summary(ToothGrowth)
```
#Plot of tooth growth vs dose
```{r}
library(ggplot2)
head(ToothGrowth)

ToothGrowth$sup <- as.character(ToothGrowth$supp)

ToothGrowth$sup[ToothGrowth$sup == "VC"] <- "VitaminC"
ToothGrowth$sup[ToothGrowth$sup == "OJ"] <- "OrangeJuice"

g <- ggplot(ToothGrowth,aes(dose,len))+geom_point(col="red")
g+facet_grid(.~ sup)+scale_x_continuous(name = "Dose (miligram/day)")+scale_y_continuous("Length Tooth Growth")+geom_smooth(method = "lm")
```
###Summary
Form the above graph it can be seen that for both Orange Juice and Vitamin C the tooth growth increases with the increase in dose.

###Mean tooth growth for each dose
```{r,eval=FALSE}
library(reshape2)
```
```{r}
meandose <- aggregate(len ~ dose,data = ToothGrowth,FUN = mean)
head(meandose)
```

###Mean tooth growth for each suppliment
```{r}
meansupp <- aggregate(len ~ supp,data = ToothGrowth,FUN = mean)
head(meansupp)
```

###Caluculating the confidence intervals for Orange Juice and Vitamin C suppliment
```{r}
orangejuice <- subset(ToothGrowth,ToothGrowth$supp == "OJ")
vitaminC <- subset(ToothGrowth,ToothGrowth$supp == "VC")
t.test(orangejuice$len - vitaminC$len)
g <- ggplot(ToothGrowth, aes(x = supp, y = len, group = factor(dose)))
g <- g + geom_line(size = 1, aes(colour = dose)) + geom_point(size =10, pch = 21, fill = "salmon", alpha = .5)
g
```


###Conclusion:
There seems a net increase in the tooth growth with the increase in the dose in each case where Orange Juice and and Vitamin C is used.
Also, the Orange juice seems to perform better than vitamin C for tooth growth

